Kaggle-in-class Data Challenges Can Boost Student Learning

### 2018-05-26 paper-kaggle.Rmd
typo

```{r likert, fig.caption="Stacked bar charts of responses to survey."}
MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")
MAST90083_likert <- MAST90083_survey %>% 
  rename(Q1=`1. I found the data competition is great fun.`) %>%
  rename(Q2=`2. Taking part in the data competition contributed a lot to my engagement with the subject.`) 
Q1 <- MAST90083_likert %>% count(Q1) %>% filter(!is.na(Q1)) %>%
  mutate(response = fct_relevel(Q1, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
  mutate(question = "Q1") %>%
  mutate(pct = n/sum(n))
Q2 <- MAST90083_likert %>% count(Q2) %>% filter(!is.na(Q2)) %>%
  mutate(response = fct_relevel(Q2, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
  mutate(question = "Q2")  %>%
  mutate(pct = n/sum(n))
Q <- bind_rows(Q1, Q2)
ggplot(Q, aes(x=question, weight = n, 
              fill=fct_relevel(response, "Strongly Disagree", 
                               "Disagree", "Neutral", "Agree", 
                               "Strongly Agree"))) + 
  xlab("") + ylab("") +
  geom_bar(position="fill") + coord_flip() +
  scale_fill_manual("", values=c("#CA0020","#F4A582","#F7F7F7","#92C5DE", "#0571B0")) +
  theme(legend.position = "bottom")
```

>>>>

```{r likert, fig.cap="Stacked bar charts of responses to survey."}
MAST90083_survey <- read_xlsx("data/Data Competition Feedback MAST90083.xlsx") %>% filter(`Email Address` != "julia.polak@unimelb.edu.au")
MAST90083_likert <- MAST90083_survey %>% 
  rename(Q1=`1. I found the data competition is great fun.`) %>%
  rename(Q2=`2. Taking part in the data competition contributed a lot to my engagement with the subject.`) 
Q1 <- MAST90083_likert %>% count(Q1) %>% filter(!is.na(Q1)) %>%
  mutate(response = fct_relevel(Q1, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
  mutate(question = "Q1") %>%
  mutate(pct = n/sum(n))
Q2 <- MAST90083_likert %>% count(Q2) %>% filter(!is.na(Q2)) %>%
  mutate(response = fct_relevel(Q2, "Strongly Disagree", "Disagree", "No Strong Feelings", "Agree", "Strongly Agree")) %>% 
  mutate(response = fct_recode(response, "Neutral" = "No Strong Feelings")) %>%
  mutate(question = "Q2")  %>%
  mutate(pct = n/sum(n))
Q <- bind_rows(Q1, Q2)
ggplot(Q, aes(x=question, weight = n, 
              fill=fct_relevel(response, "Strongly Disagree", 
                               "Disagree", "Neutral", "Agree", 
                               "Strongly Agree"))) + 
  xlab("") + ylab("") +
  geom_bar(position="fill") + coord_flip() +
  scale_fill_manual("", values=c("#CA0020","#F4A582","#F7F7F7","#92C5DE", "#0571B0")) +
  theme(legend.position = "bottom")
```
